---
title: "Mini-Project 2"
author: "Anjali Desai, Prayasha Chaudhary, Ariana Meredith"
date: "March 24, 2017"
output: html_document
---


## Loading the data and Libraries 

```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")

library(tidyverse)
library(ggplot2)
library(dplyr)
```
 - use house_elections data to find the relation between the number of votes given to republican vs. democratic candidates 
 
## Sorting the data
```{r}

Cand <- candidates %>%
  select(cand_id, cand_name, cand_party_affiliation, cand_election_yr)  %>%
  filter(cand_party_affiliation == c("DEM", "REP"), cand_election_yr == 2012) %>%
  #filter(cand_party_affiliation == "DEM" ,cand_election_yr >= 2000, cand_election_yr <=2012) %>%
  arrange(cand_election_yr)
#Cand

x <- rename(Cand,  fec_id = cand_id)

House <- house_elections %>%
  select(fec_id, primary_votes, general_votes, state) %>%
  filter(state == c("ME" ,"NH" , "VT", "MA", "RI", "CT", "NY", "NJ", "PA"))
House
joined <- x %>% inner_join(House,  by = "fec_id")
joined
```
- What are we graphing?
Based on party (REP or DEM), whether candidates that were in office stayed in office
So if incumbent == true, that means they were running for re-election,
and ge_winner indicates N or W, where W == won.

## Creating the graph
```{r}
ggplot(data = joined, aes( x= state, y=primary_votes, fill = cand_party_affiliation))+ geom_bar(stat = "identity")
ggplot(data = joined, aes( x= state, y=general_votes, fill = cand_party_affiliation))+ geom_bar(stat = "identity")

```

## Summarize the results
```{r}

```

