---
title: "Mini-Project 2"
author: "Anjali Desai, Prayasha Chaudhary, Ariana Meredith"
date: "March 24, 2017"
output: html_document
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE) #hide error messages etc.
```

```{r, include=FALSE}
##Loading the data and libraries 

library(ggmap)
library(maps)
library(mapdata)

load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")

library(tidyverse)
library(ggplot2)
library(dplyr)
```

 
## Sorting the data
```{r}

Cand <- candidates %>%
  select(cand_id, cand_name, cand_party_affiliation, cand_election_yr)  %>%  #selecting the variables we want (id, name, party, year)
  filter( cand_election_yr == 2012) %>% #filter for just 2012
  arrange(cand_name)

House <- house_elections %>%
  select(fec_id, general_votes, state, candidate_name, party) %>% #selecting the variables we want (id, votes, state, name, party)
  filter(state == "ME" |state =="NH" |state == "VT"|state == "MA"|state == "RI"|state == "CT"|state == "NY"| state =="NJ"| state =="PA") #filtering for northeast states

x <- rename(Cand,  fec_id = cand_id) #renaming cand_id to fec_id so the id variable name matches for the join

joined <- x %>% inner_join(House,  by = "fec_id") %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") #filter for democrats or repbulicans only

joined

```

## Creating the graph
```{r}
ggplot(data = joined, aes( x= state, y=general_votes, fill = cand_party_affiliation))+ geom_bar(stat = "identity") + labs(x = "Year", y = "General Votes") + scale_fill_manual(values =c("Blue","Red"), name = "Guide", breaks=c("DEM", "REP"))

```

This graph shows states in the Northeast and looks at the general election votes in that state for the house elections of 2012, grouped by the party affiliation (Republican or Democrat) of the candidate that the votes went to.

## Analyzing the Results

The data shows that Democratic Candidates seems to receive more votes than Republican Candidates do in the Northeast for the House elections. 

This poll history (http://www.gallup.com/poll/15370/party-affiliation.aspx) shows that Americans seems to historically identify roughly equally as either a Republican or a Democrat. For example, the most recent poll shows that 31% of Americans identify as Republican, and 31% identify as Democrat. If we look back to June 2012, the year of our data, it shows again an equal percentage (30%) of Americans that consider themselves either a Democrat or Republican. 

The third choice in the poll is Independent, and more Americans consistently identify as Independent than one of two other parties, with about 40% of Americans considering themselves Independents.

Since the amount of Americans who consider themselves a Democrat or Republican is roughly equal, one explanation of why Democratic candidates seem to receive more votes than Republican Candidates is because Independent voters tend to vote more for Democratic Candidates than Republican Candidates, and since they represent a large percentage of voters, they can easily influence the proportion of votes. 

The Northeast is also known to be a more left-leaning region than other areas of the United States, so it is not surprising that our data reveals that Democratic candidates tended to receive more votes in the Northeast. 


